State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-02 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to figure 1

%The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to the generate data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. An example of the simulated field can be seen in figure~\ref{fig:experimental design}~A. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum). This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{fig:experimental design}~B. shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C. shows the power spectral density of on of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.

@@

\begin{figure}[!hb] 
% \renewcommand*{\thesubfigure}{}
\centering
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \hspace{2.5mm}
\subfigure{\includegraphics[width=2in]{./Graph/ExperimentFigurePSDPy.pdf}}
\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}

\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.

@@

\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform. We used a one-step Euler method where Eq.~\ref{FinalForm1} can be approximated by 

>>>>

%The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
\section{Results}\label{ResultsSection} The neural field model derived in section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. An example of the simulated field can be seen in figure~\ref{fig:experimental design}~A. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field (full width at half maximum). This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{fig:experimental design}~B. shows example data from the sensors of the model, and figure~\ref{fig:experimental design}~C. shows the power spectral density of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.

@@

\begin{figure}[!hb]
\centering
\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy.pdf}}\\
% \hspace{2.5mm}
\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \hspace{2.5mm}
\subfigure[]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}}
\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:experimental design} 
\end{figure}
\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}\\
\caption{Distribution of the parameters estimates over 272
runs.}
\label{fig:Parameters}
\end{figure}
\subsection{Spatial Frequency Analysis} In accordance with Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{} shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \omg{??}, which corresponds to the \omg{??-3~dB} from the peak power. From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \omg{??}. This confirms our separation was enough to prevent problems associated with aliasing.

@@

\section{Discrete Time Model}\label{Time Discretization} To form the IDE neural field model a time discretization must be perform. We used a one-step Euler method where Eq.~\ref{FinalFormContinuous} can be approximated by 
